\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage[parfill]{parskip}
\geometry{a4paper, margin=0.75in}

\pagenumbering{gobble}

\newcommand{\textwithhr}[1]{
\textsc{#1}

\vspace{-5mm} \hrulefill
}

\begin{document}

\begin{center}
    \huge{\textbf{Todor Dukov}}

    \normalsize{+359 882 700 671 $\mid$ \href{mailto:todor@dukov.net}{todor@dukov.net} $\mid$ \href{https://github.com/toduko}{\faGithubSquare \, todukov} $\mid$ \href{https://www.linkedin.com/in/todor-dukov}{\faLinkedinSquare \, Todor Dukov}}
\end{center}

\textwithhr{Education}

\textbf{B.Sc. in Computer Science, Sofia University “St. Kliment Ohridski”} \hspace*{\fill} \textit{10/2021 -- 07/2025}

\begin{itemize}
    \item Achieved \textbf{5.75/6.00} overall GPA
    \item Scored \textbf{6.00/6.00} on the State Examination
\end{itemize}

\textbf{Teaching Experience:}
\begin{itemize}
  \item \textbf{Languages, Automata, and Computability} (4 semesters):  
        Delivered seminars on finite automata, regular expressions, context-free grammars, pushdown automata, and Turing machines.
  \item \textbf{Design and Analysis of Algorithms} (1 semester):  
        Covered asymptotic analysis, algorithm correctness and completeness, lower bounds, and computational complexity theory.
  \item \textbf{Logic Programming} (1 semester):  
        Taught first-order logic definability and satisfiability, Prolog programming, and resolution methods for predicate logic.
\end{itemize}

\textwithhr{Professional Experience}

\textbf{Junior Software Engineer, MBition} \hspace*{\fill} \textit{01/2025 -- Present}  

I engineer embedded software solutions for part of the \textbf{Mercedes-Benz} vehicle systems in accordance with the \textbf{AUTOSAR Classic (MICROSAR Classic)} standard, ensuring high reliability, scalability, and maintainability.  
I am responsible for developing Base Layer Software for both the Application and Flash Bootloader modules of our team's ECUs using \textbf{DaVinci Configurator} and for integrating with \textbf{CANoe} to perform simulation and validation.  
I also develop automation tools by writing \textbf{Groovy} scripts for configuration processes, \textbf{Python} scripts for software flashing and internal development tools, and \textbf{Bash} scripts to streamline internal toolchains.  
I collaborate closely with cross-functional teams to optimize system performance, reduce integration time, and ensure smooth deployment.  

\textbf{Junior Part-Time Software Engineer, Intellics Engineering} \hspace*{\fill} \textit{02/2022 -- 06/2022}  

I designed and implemented a mobile application using \textbf{Vue.js}, \textbf{Cordova}, and \textbf{Firebase} to streamline the scheduling and coordination of football games for social groups.  
I independently managed feature development and debugging to ensure the application functioned smoothly.  

\textbf{Software Engineering Intern, Programista} \hspace*{\fill} \textit{11/2020 -- 12/2020}  

I contributed to the development of a mobile coding education platform by implementing authentication and real-time database functionality with \textbf{Kotlin} and \textbf{Firebase}.  
I actively applied best practices in coding and testing to maintain the platform's quality.

\textbf{Software Engineering Intern, Musala Soft} \hspace*{\fill} \textit{06/2020}  

I completed a two-week intensive internship that included seminars on modern software development practices.  
I developed a real-time video chat application using \textbf{React} and \textbf{Express.js}, integrating WebRTC to enable peer-to-peer communication.  

\textbf{Software Engineering Intern, Proxiad Bulgaria} \hspace*{\fill} \textit{01/2020 -- 03/2020}  

I developed a multiplayer Hangman game with \textbf{Express.js} and \textbf{React} as part of my introduction to full-stack web development.  
I also gained hands-on experience working with \textbf{Spring Boot} and \textbf{React} in a collaborative team environment.

\textwithhr{Skills}

\begin{multicols}{2}
\noindent
\textbf{Programming Languages:} \\
C, C++, Python, Groovy, Bash, Kotlin, JavaScript, TypeScript, Java, GDscript, Vimscript, Haskell, Scheme, Prolog

\vspace{0.3em}

\textbf{Frameworks \& Libraries:} \\
Pygame, Tkinter, Vue.js, React.js, Apache Cordova, Express.js, Mongoose, Spring Boot, Jest, SFML, Raylib

\vspace{0.3em}

\textbf{Embedded Systems \& Standards:} \\
AUTOSAR Classic (MICROSAR Classic), DaVinci Configurator, CANoe

\vspace{0.3em}

\textbf{Databases \& Backend:} \\
Firebase, REST APIs, MySQL, MongoDB

\vspace{0.3em}

\textbf{Tools \& Platforms:} \\
Git, Repo, Docker, Linux, JIRA, Make, CMake

\end{multicols}

\end{document}
